### 2016-05-02 response.txt

We thank the reviewers for very helpful comments.

R1:

Q: ...do you observe a correlation between distinct test cases and distinct invariants?

Even reduced test cases are hard to connect to invariants, tend to execute 10K+ LOC (see https://github.com/agroce/mutants16/tree/master/tests).  There probably is a correlation, but it's hard to spot for compiler faults.  We'd definitely like to investigate further.

Q: ...all bugs... due to... optimizations. Is this correct? ...do these... the majority of bugs...? ...results to change for non-compiler benchmarks?

For GCC ~90% of faults detected by changing from -O0 to -O3, so seems to be the rule for GCC.  For SpiderMonkey, "optimization" is hard to separate from odd JavaScript semantics, or attempts to speed up SpiderMonkey in general (not neccessarily code optimization exactly).  Results of Qi et al. suggest many programs _can_ be "patched" by turning off a feature, which is promising.

3) Section 1.2: “if two failures.., baseline probability*. What does this mean?

(Baseline) B = chance two failing tests are due to same fault.  Knowing two failures are "fixed" by turning off same optimization indicates probability they are same fault is > B.  We quantify (for our subjects) how much this holds (though not for optimization changes alone).

R2:

Q: ...fault of the center... repairs many others? Will that fault be discovered?

Really depends on the overall structure (what repairs those other tests).

Q: ...faults not discovered in the experiment...?

No obvious patterns, but differences would be complex properties of C/JavaScript and GCC/SpiderMonkey.  We'll investigate further.

Q: ...sampling does alter the results... undesirable happening in terms of the onion ring model.

Sampling hurts localization, there are probably ways to do good sampling for fuzzer taming (we are investigating).  Our guess: localization is bad when nothing in the middle of the onion ring is left, and that set could be small.

We'll provide numbers on runtimes (JavaScript not bad, GCC pretty bad, but we ran build/mutants in a very inefficient way).

R3:

Q: ...what kind of changes... ...does that count?  ...insert System.exit(0) at the beginning...?

Anything such that the test oracle passes is allowed.  For a very weak oracle, you could get away with this.  Due to onion ring, letting some "silly" changes make tests pass is probably harmless, so long as other more interesting mutants are also used.

Q: ...don’t quite understand... evaluation results...

Figure 2 shows _only_ fuzzer taming results, Tables 1-2 are _only_ for localization results.  These are two different goals, and evaluated separately.  FPF value only in Tables to show that how well a fault localizes and how well it is identified seem (surprisingly) unrelated.

Q: ...role of passing tests is "lower" than that of failing tests?

We believe so: probably for fuzzer taming, possibly for localization (note MUSEUM and other localizations agree).  Faulty code often executes in many passing tests; determining conditions for failure is difficult.  There is more information _about faults_ in failures, in some sense: e.g., single failing test can show a fault exists, which all passing tests cannot!

Q: ...how to interpret... Figure 3...

992 (commented "ADDED") is part of the code in the patch, as is the deleted statement (line #s in patch would help).  We'll clarify this much better, sorry!  3/6 is indeed ranked change.

Q:  ...confirm that these 8 faults are correct...?

For these 8 (and 16 GCC faults), we had a backpatch, based on commit data and comments, and tested it.  The other faults had such complex change history this was not feasible, making localization (not taming) evaluation impossible.  Backpatch sets were produced by colleagues, not us, before we began this work (so are not cherry-picked).

### 2016-05-02 response.txt

We thank the reviewers for very helpful comments.

R1:

Q: ...do you observe a correlation between distinct test cases and distinct invariants?

Even reduced test cases are hard to connect to invariants, tend to execute ~10-50K+ LOC (see https://github.com/agroce/mutants16/tree/master/tests).  There probably is a correlation, but it's hard to spot for compiler faults.  We'd definitely like to investigate further.

### 2016-05-02 response.txt

Q: ...faults not discovered in the experiment...?

No obvious patterns, but differences would be complex properties of C/JavaScript and GCC/SpiderMonkey.  We'll investigate further.

Q: ...sampling does alter the results... undesirable happening in terms of the onion ring model.

Sampling hurts localization, maybe mostly ok for taming (we're investigating more).  Our guess: localization is bad when nothing in the middle of the onion ring is left (could be small set), which taming can handle.

We're very interested in alternatives to general mutation, thanks for ideas!

Will provide runtimes (JavaScript ok, GCC bad, but we ran/built mutants in inefficiently).

### 2016-05-02 response.txt

Q: ...do you observe a correlation between distinct test cases and distinct invariants?

Even reduced test cases are hard to connect to invariants, tend to execute ~10-50K+ LOC (see https://github.com/agroce/mutants16/tree/master/tests).  There probably is a correlation, but it's hard to spot for compiler faults.  We'd definitely like to investigate further.

Q: ...all bugs... due to... optimizations. Is this correct? ...do these... the majority of bugs...? ...results to change for non-compiler benchmarks?

~90% of GCC faults detected by changing from -O0 to -O3, so seems to be the rule for GCC.  For SpiderMonkey, "optimization" hard to separate from odd JavaScript semantics, or attempts to speed up SpiderMonkey in general (not always traditional optimization).  Results of Qi et al. suggest many programs _can_ be "patched" by turning off a feature, at least; MUSEUM also suggests generalization plausible.

@@

3) Section 1.2: “if two failures.., baseline probability*. What does this mean?

(Baseline) B = chance two failing tests are due to same fault.  Knowing two failures are "fixed" by turning off same optimization indicates probability they are same fault is > B.  We quantify (for our subjects) how much this holds (though not for optimizations alone).

@@

Q: ...sampling does alter the results... undesirable happening in terms of the onion ring model.

Sampling hurts localization, maybe mostly ok for taming (we're investigating more).  Our guess: localization is bad when nothing in the middle of the onion ring is left (could be small set), which taming can handle.

We're very interested in alternatives to general mutation, thanks for ideas!

Will provide runtimes (JavaScript ok, GCC bad, but we ran/built inefficiently).

@@

R3:

TACAS04 uses a _very_ different metric, in a very different way, we believe.

Q: ...what kind of changes... ...insert System.exit(0)...?

@@

Anything such that the test oracle passes is allowed.  For a very weak oracle, you could get away with this.  Due to onion ring, letting some "silly" changes make tests pass is probably harmless, so long as other more interesting mutants are also used.

Q: ...don’t quite understand... evaluation results...

Figure 2 shows _only_ fuzzer taming results, Tables 1-2 are _only_ for localization results.  These are _different_ goals, both using the metric.  FPF value only in Tables to show that how well a fault localizes and how well it is identified seem (surprisingly) unrelated.

Q: ...role of passing tests... "lower" than... failing tests?

We believe so: probably for fuzzer taming, possibly for localization (MUSEUM and other localizations agree).  Faulty code often executes in many passing tests; determining conditions for failure is difficult; thus more information _about faults_ in failures, in some sense: e.g., single failing test can show a fault exists, which all passing tests cannot!

### 2016-05-02 response.txt

Q: ...all bugs... due to... optimizations. Is this correct? ...do these... the majority of bugs...? ...results to change for non-compiler benchmarks?

~90% of GCC faults detected by changing from -O0 to -O3, so seems to be the rule for GCC.  For SpiderMonkey, "optimization" hard to separate from odd JavaScript semantics, or attempts to speed up SpiderMonkey in general (not always traditional optimization).  Results of Qi et al. suggest many programs _can_ be "patched" by turning off a feature, at least; MUSEUM also suggests generalization plausible.

3) Section 1.2: “if two failures.., baseline probability*. What does this mean?

(Baseline) B = chance two failing tests are due to same fault.  Knowing two failures are "fixed" by turning off same optimization indicates probability they are same fault is > B.  We quantify (for our subjects) how much this holds (just not for optimizations alone).

@@

We're very interested in alternatives to general mutation, thanks for ideas!

Will provide runtimes (JavaScript ok, GCC bad, but we ran/built inefficiently).

R3:

TACAS04 uses a completely different metric, in a very different way, we believe.

### 2016-05-03 response.txt

Q: ...all bugs... due to... optimizations. Is this correct? ...do these... the majority of bugs...? ...results to change for non-compiler benchmarks?

~90% of GCC faults detected by changing from -O0 to -O3, so seems to be the rule for GCC.  For SpiderMonkey, "optimization" hard to separate from odd JavaScript semantics, or attempts to speed up SpiderMonkey in general (not always traditional optimization).  Results of Qi et al. suggest many programs _can_ be "patched" by turning off a feature, at least; MUSEUM also suggests generalization plausible.

3) Section 1.2: “if two failures.., baseline probability*. What does this mean?

(Baseline) B = chance _any_ two failing tests are due to same fault.  Knowing two failures are "fixed" by turning off same optimization indicates probability they are same fault is > B.  We quantify (for our subjects) how much this holds (just not for optimizations alone).

@@

Q: ...how to interpret... Figure 3...

992 (commented "ADDED") is part of the code in the patch, as is the deleted statement (line #s in patch would help).  We'll clarify this much better, sorry!  3/6 is indeed ranked change.

Q:  ...confirm that these 8 faults are correct...?

For these 8 (and 16 GCC faults), we had a backpatch, based on commit data and comments, and tested it.  The other faults had such complex change history this was not feasible, making localization (not taming) evaluation impossible.  Backpatch sets were produced by colleagues, not us, before we began this work, to avoid bias.

### 2016-05-03 response.txt

We thank the reviewers for very helpful comments.

R1:

...significant over PLDI 2013...

Using our samplings and top-N PLDI 13 results (non-ideal method, hence not in paper), results _are_ _statistically_ significant (know not what you meant, but worth noting).

Q: ...correlation between... test cases and... invariants?

Even reduced test cases are hard to connect to invariants, tend to execute ~10-50K+ LOC (https://github.com/agroce/mutants16/tree/master/tests).  Probably is a correlation, but it's hard to spot for compiler tests.  We'll definitely investigate further!

Q: ...optimizations... majority of bugs...? ...non-compiler benchmarks?

~90% of GCC faults detected by changing from -O0 to -O3, so seems to be the rule for GCC.  For SpiderMonkey, "optimization" hard to separate from odd JavaScript semantics, or attempts to speed up SpiderMonkey in general (not always traditional optimization).  Results of Qi et al. suggest many programs _can_ be "patched" by turning off a feature; MUSEUM results also suggest generalization plausible.

3) ...baseline probability. What does this mean?

(Baseline) B = chance _any_ two failing tests are due to same fault.  Knowing two failures are "fixed" by turning off same optimization indicates probability they are same fault is > B.  We quantify (in 4.1, 4.2) this claim (though not for optimizations alone).

@@

R2:

Q: ...center... repairs many others? Will that fault be discovered?

Really depends on the overall structure (what repairs which other tests).

@@

Q: ...faults not discovered in the experiment...?

No obvious patterns, but differences would be complex properties of C/JavaScript and GCC/SpiderMonkey.  We'll investigate further!

Q: ...sampling does alter the results... undesirable happening in terms of the onion ring model.

Sampling hurts localization, maybe ok for taming (we're investigating).  Our guess: localization is bad when nothing in the middle of the onion ring is left (could be small set), which hurts taming less.

@@

We're very interested in alternatives to general mutation, thanks for ideas!

Will provide runtimes (JavaScript ok, GCC bad, but we ran/built inefficiently).

R3:

TACAS04 is completely different metric, used very differently, we believe.

@@

Q: ...what kind of changes... ...insert System.exit(0)...?

Anything such that the test oracle passes is allowed.  For a very weak oracle, you could get away with this.  Due to onion ring, letting some "silly" changes make tests pass is probably harmless, so long as other more interesting mutants are also used.

Q: ...don’t quite understand... evaluation results...

Figure 2 shows _only_ fuzzer taming results, no localization; Tables show _only_  localization results.  These are _independent_ goals, using same metric.  FPF column only in Tables to show that how well a fault localizes and how well it is identified seem (surprisingly) unrelated.

### 2016-10-19 localizations.tex
more edits
fixed bad exp of localization

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change is
limited to changes in program state and data values.  However, the
vast majority of mutant repairs also modify the code coverage of a
test; in our experiments, there were no repairs that did not change
coverage.  If a fault can be avoided by, for example, avoiding a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
  coverage changed most often in repairs.  Early experiments with this
  approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

@@

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant statement also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.

>>>>

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change is
limited to changes in program state and data values.  However, the
vast majority of mutant repairs also modify the code coverage of a
test; in our experiments, there were no repairs that did not change
coverage.  If a fault can be avoided by, for example, disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
  coverage changed most often in repairs.  Early experiments with this
  approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

@@

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failng test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.
